Autonomous Oceanographic Data Collection towards Estimating Excursion Sets of Vector-valued Random Fields

### 2020-06-16 main_new.tex
Updates from Overleaf

\section{Simulation study}
\label{sec:simulations}

We now study the properties of the different static and sequential
survey designs in a realistic case that emulates the spatial
properties of a river plume interacting with coastal water.

\subsection{Modeling}

A GP model is used to represent the bivariate random fields of
temperature and salinity. At location $\x \in \mathcal{M}$, the
bivariate distribution is:
\begin{equation}\label{gp_bar}
\begin{bmatrix}Z_1(\x) \\
Z_2(\x) \end{bmatrix}
\sim N \left( 
\begin{bmatrix} \mu_{1}(\x)\\
\mu_{2}(\x)
\end{bmatrix},\begin{bmatrix}
\sigma_{1}^2 & \sigma_{1} \sigma_2 \gamma \\
\sigma_{1} \sigma_2 \gamma  & \sigma_{2}^2 
\end{bmatrix}
\right).
\end{equation}
We specify the mean by $\mu_{1}(\x)=5.8 + 0.065 u_{\mbox{West}}$ and
$\mu_{2}(\x)=29 + 0.1 u_{\mbox{West}}$, which means that the expected
levels of both temperature and salinity increase linearly in the
western direction.  This situation mimics that of a river mouth
opening from the south, with the water masses pulled to the east by
the Coriolis force \kc{This seems overly specific to the Nidelva use
  case. Can it be generalized, after all that is the overall intent of
  this manuscript?}.  The variances are set to $\sigma_1=0.25$ and
$\sigma_2=0.6$, while the correlation is $0.6$.  The spatial
correlation is of separable Matern type (see e.g. \cite{Cressie:11})
so that
\begin{equation}\label{v}
\small
\mbox{Corr} 
\left(
\begin{bmatrix}
    Z_1(\x) \\
    Z_2(\x) 
    \end{bmatrix},
    \begin{bmatrix}
    Z_1(\x') \\
    Z_2(\x') 
    \end{bmatrix}
    \right)
    = \begin{bmatrix}
1 & 0.6  \\
0.6  & 1
\end{bmatrix}(1+\phi h)\exp (-\phi h),
\end{equation}
where $h=\sqrt{||\x-\x'||^2}$ and $\phi=0.3$ indicates an effective
correlation range of about $1200$ m.

In the accompanying Python code, these modeling assumptions can be
generalized to anisotropic covariance and changing variance levels
across the spatial domain. One can hence, easily run the code to see
if different models result in other sampling designs. Anisotropy and
non-stationary variance are both relevant for the setting with river
plumes, but in practice this requires more parameters to be
specified. With extensive data and prior knowledge, one could also
possibly fit and estimate parameters of more complex multivariate
spatial covariance functions
\citep{gneiting2010matern,genton2015cross}, but that is outside the
scope of the current paper.

We discretize the spatial domain $\mathcal{M}$ to a set of $n$ grid
locations $\mathcal{M}_g = \{\x_i, i=1,\ldots,n \}$, \kc{is the index
  correct? TeX shows it as u or g for $\mathcal{M}$} where each cell
has area $\Delta$; the same grid is used for the waypoint graph for
possible design locations. The EIBV is approximated by sums over all
grid cells.

One realization of the random fields representing salinity and
temperature is shown in Fig. \ref{fig:true_temp} and
\ref{fig:true_sal}. The true ES is a realization from this model as
shown in Fig. \ref{fig:ESet}.

\begin{figure}[!h]
  \centering
  \subfigure[Simulated temperature.]{\includegraphics[height = 0.40\textwidth]{Figures/sim/true_temp.pdf}\label{fig:true_temp}}
  \hfill
  \subfigure[Simulated salinity.]{\includegraphics[height = 0.40\textwidth]{Figures/sim/true_sal.pdf}\label{fig:true_sal}}
  \hfill
  \subfigure[Excursion set given the realization of temperature and salinity.]{\includegraphics[height = 0.40\textwidth]{Figures/sim/es_ts_true.pdf}\label{fig:ESet}}
  \hfill
  \subfigure[Excursion probabilities given collected data using the
  `static\_north" strategy.]{\includegraphics[height = 0.40\textwidth]{Figures/sim/es_ts_posterior.pdf}\label{fig:Eprob}}
  \caption{\ref{fig:true_temp} and \ref{fig:true_sal} show a
    realization of the simulated temperature and salinity fields. The
    associated ES is in \ref{fig:ESet}, while \ref{fig:Eprob} shows
    the estimated EPs after performing data collection along the
    static N-S survey line.}
\label{fig:realisations}
\end{figure}

\subsection{Static and Sequential Sampling Designs}
\label{sec:sampling_designs}

@@

\begin{figure}[!b]
  \centering
  \subfigure[Look-ahead]{\includegraphics[height = 0.46\textwidth]{Figures/sim/route_look-ahead.pdf}\label{fig:avg_look-ahead}}
  \hfill
  \subfigure[Myopic]{\includegraphics[height = 0.46\textwidth]{Figures/sim/route_myopic.pdf}\label{fig:avg_myopic}}
  \hfill
  \subfigure[Naive]{\includegraphics[height = 0.46\textwidth]{Figures/sim/route_naive.pdf}\label{fig:route_naive}}
  \hfill
  \subfigure[Static]{\includegraphics[height = 0.46\textwidth]{Figures/sim/route_static.pdf}\label{fig:route_static}}
  \hfill
  \caption{The overlaid route choices (strategies), superimposed on
    the 100 replicate surveys with 10 sampling choices/stages. \kc{I
      would reorder these figurs above based on the order the material
      was discussed -- Static, naive, myopic and then Look-ahead. Also
      do you really need a key associated with each subfigure, given
      the caption? An abridged analysis as in the text, might also be
      in order here in the caption. Also refer to
      Fig. \ref{fig:realisations} as the reference, where the
      temp/salinity fields are shown.}}
\label{fig:route_choices}
\end{figure}

>>>>

\subsection{Simulation study}
\label{sec:simulations}

\susubsection{Static and Sequential Sampling Designs}
\label{sec:sampling_designs}

@@
